Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2018-12-26 paper/ms.tex
Update paper

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{Caption.}
\label{fig:rand_deltaphi}
\end{figure*}

@@

With a characteristic $z$ offset in hand, we consult Figure~\ref{fig:deltaphi}
to convert this $z$ offset into a $\Delta \phi$, which we convert to an
arclength or characteristic distance (the difference between the two will be
negligible for the small $\Delta \phi$'s we will compute). Therefore, if an
observer is attempting to reconstruct a cluster with a given mass on a given
orbit, we will give a characteristic distance between a field star and the
cluster within which an observer might not need to consider differences in
their respective local midplanes.

@@

We use the relation in Figure~\ref{fig:deltaphi}, which shows the typical $z$
offset at each $\Delta \phi$, to convert a given $z$ offset into a $\Delta
\phi$, which we then convert into a chord length which we interpret as
$R_{\n}$.

>>>>

\begin{figure*}
\plotone{fig/range_dphi.pdf}
\caption{Caption.}
\label{fig:range_deltaphi}
\end{figure*}

@@

With a characteristic $z$ offset in hand, we consult
Figure~\ref{fig:range_deltaphi} to convert this $z$ offset into a $\Delta
\phi$, which we convert to an arclength or characteristic distance (the
difference between the two will be negligible for the small $\Delta \phi$'s we
will compute). Therefore, if an observer is attempting to reconstruct a
cluster with a given mass on a given orbit, we will give a characteristic
distance between a field star and the cluster within which an observer might
not need to consider differences in their respective local midplanes.

@@

We use the relation in Figure~\ref{fig:range_deltaphi}, which shows the
typical $z$ offset at each $\Delta \phi$, to convert a given $z$ offset into a
$\Delta\phi$, which we then convert into a chord length which we interpret as
$R_{\n}$. The result of this procedure is shown in Figure~\ref{fig:Rn_mc}.

\begin{figure*}
\plotone{fig/}
\end{figure*}
